Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-26 README.Rmd
explanation of comparison features

A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX). It contains comparisons from `r length(unique(bullet_train$land_id1))` bullet-land signatures with some lands missing due to tank rash or other reasons. This dataset is created using the data available at XXX, which contains XXX. The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons. The variables in the data are as follows:

- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison.
- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'.
- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'.
- `r names(bullet_train)[4]` = the comparison feature of two signatures of cross correlation.
- `r names(bullet_train)[5]` = the comparison feature of two signatures of rough correlation.
- `r names(bullet_train)[6]` = the comparison feature of two signatures of distance.
- `r names(bullet_train)[7]` = the comparison feature of two signatures of standard deviation of distance.
- `r names(bullet_train)[8]` = the comparison feature of two signatures of matches.
- `r names(bullet_train)[9]` = the comparison feature of two signatures of mismatches.
- `r names(bullet_train)[10]` = the comparison feature of two signatures of consecutively matched striae.
- `r names(bullet_train)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
- `r names(bullet_train)[12]` = the comparison feature of two signatures of sum of peaks.
- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match.
- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match.

For further details about the signatures comparison features, see XXX.

@@

A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The variables in the data are as follows:

- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison.
- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
- `r names(bullet_test)[4]` = the comparison feature of two signatures of cross correlation.
- `r names(bullet_test)[5]` = the comparison feature of two signatures of rough correlation.
- `r names(bullet_test)[6]` = the comparison feature of two signatures of distance.
- `r names(bullet_test)[7]` = the comparison feature of two signatures of standard deviation of distance.
- `r names(bullet_test)[8]` = the comparison feature of two signatures of matches.
- `r names(bullet_test)[9]` = the comparison feature of two signatures of mismatches.
- `r names(bullet_test)[10]` = the comparison feature of two signatures of consecutively matched striae.
- `r names(bullet_test)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
- `r names(bullet_test)[12]` = the comparison feature of two signatures of sum of peaks.
- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match.
- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match.

For further details about the signatures comparison features, see XXX.

@@

Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:

- `r names(signatures)[1]` = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
- `r names(signatures)[2]` = The x position of the signature
- `r names(signatures)[3]` = The y position of the signature

>>>>

A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby]. This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/). 
It contains comparisons from `r length(unique(c(bullet_train$land_id1, bullet_train$land_id2)))` bullet-land signatures. 12 of the overall 420 lands (6 lands per bullets, 35 bullets in each set) are excluded from the comparison. Six of these lands show so-called "tank rash" - damage to the bullets after it exited the barrel (see [tank rash scans](LEAscans/tankrash.md)). Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from (see [scans from bullet E](LEAscans/bullete.md)). 
The <b>bullet_train</b> data is based on a set of features extracted from the x3p scans as described in @hare:2016. The raw file of comparison features is found [here](data/raw/hamby-comparisons.csv.zip). The only changes made to the data were XXX I think the following statement needs to be adjusted XXX to select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons. The variables in the data are as follows:

#### Variables used as key variables:
- `r names(bullet_train)[1]`: ID number associated with the bullet-land signature comparison.
- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is 'study - barrel number - bullet number - land number'.

#### Comparison features
- `r names(bullet_train)[4]`: maximized cross-correlation between two LEA signatures.
- `r names(bullet_train)[5]`: correlation after detrending aligned signatures.
- `r names(bullet_train)[6]`: Euclidean distance (in millimeters) between two aligned signatures.
- `r names(bullet_train)[7]`: standard deviation of the previous measure along the signature.
- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: number of matching/non-matching peaks and valleys in the aligned signatures.
- `r names(bullet_train)[10]`: consecutively matching striae is a measure introduced by @biasotti describing the longest run of matching peaks between two aligned signatures.
- `r names(bullet_train)[11]`: the number of consecutively non-matching peaks.
- `r names(bullet_train)[12]`: the depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
- `r names(bullet_train)[13]`: ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).
- `r names(bullet_train)[14]`: the random forest score associated with the comparison in support of a match.

<!--For further details about the signatures comparison features, see XXX.-->

@@

A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone sets. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Similar to the training set, each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The variables in the test data are the same as the training data described above.

<!-- For further details about the signatures comparison features, see XXX.-->

@@

Contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:

- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to 'Signature 1' or 'Signature 2'
- `r names(signatures)[2]`: the (relative) x position of the signature (in microns)
- `r names(signatures)[3]`: the (relative) y position of the signature height (in microns)
